---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
  knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# <img src="https://cdn.jsdelivr.net/npm/bootstrap-icons/icons/rocket-takeoff-fill.svg" width="20"> `{PathCast}`

<!-- badges: start -->
<!-- badges: end -->

## What is PathCast?

**PathCast** is an educational and exploratory data analysis tool designed to support the development of machine learning frameworks—specifically for diffusion process classification and parameter estimation.

### PathCast has three main goals:

- **Introduce diffusion processes in an accessible way**  
  - Current focus includes: Geometric Brownian Motion (GBM), Ornstein-Uhlenbeck (OU), and OU with jumps.

- **Highlight unique characteristics of each process**  
  - What components are deterministic vs. probabilistic?  
  - What tools can help us classify a process?  
  - What assumptions underlie each model, and how can we address their limitations?

- **Explore how machine learning can enhance decision-making**  
  - How do we quantify confidence in our classifications and parameter estimates?  
  - What would a manual classification process look like—and how could ML improve it?

### Future Development Plans

- Develop and test machine learning algorithms  
  - Focus on improving process classification, parameter estimation, and strategy selection

- Reverse-engineer trading strategies using classified processes and estimated parameters  
  - Understand how specific dynamics influence strategic decisions

- Use process parameters to simulate strategy performance  
  - Assess robustness under different stochastic regimes

- Screen for similar processes across a market universe  
  - Identify clusters of assets with comparable dynamics to build a diverse, tradeable strategy
  
  

## Installation

You can install the development version of `{PathCast}` like so:

```{r, eval=FALSE}
devtools::install_github('MoneyMG/PathCast')
```

Docker image also available via dockerhub:

[Pathcast on Docker Hub](https://hub.docker.com/r/magad1/pathcast)

## Run

You can launch the application by running:

```{r, eval = FALSE}
PathCast::run_app()
```

## About

You are reading the doc about version : `r golem::pkg_version()`

This README has been compiled on the

```{r}
Sys.time()
```

package coverage:

```{r echo = FALSE}
unloadNamespace("PathCast")
```

```{r, error = TRUE}
covr::package_coverage()
```
